DPSh: Automated Data-Parallel Processing in the Shell

### 2020-03-21 pldi/draft.tex
Note
Update
New introduction

%% Title information
\title{Dish: Distribution-oblivious Shell Scripting}         %% [Short Title] is optional;
%% \title{Extensible data processing in the shell}

@@

@@

Key tasks, in rough order of importance:
  (i) change title and intro to avoid distribution
  (ii) cleanup and rewrite sections 4, 5: introduce our high-level figure, talk
  about things in order, add ordering in graphs, generally refine and beautify
  as much as possible.
  (iii) tighten section 2, everything in there has to be related to some part of
  the story---make the connection explicit
  (iv) Pump up evaluation: could we add 3 more micro-benchmarks? could we add
  1--2 more macro-benchmarks?
  (v) since this is IFCP, could we add some simple semantics and derivation
  rules? we should certainly be able to describe some of the optimizations as
  congruence rules.
  (vi) complete the related work with some operating-systems literature.
}

\kk{After discussion on Wednesday Jan 8: Modify the narrative of this
  paper to talk about data processing in the Shell. Make this the main
  focus of the paper. This simplifies the narrative and allows us to
  not talk about late planner activation as well as environment
  variables. It also justifies why we only deal with pure and
  stateless. Note that this is a very expressive model, as shown by
  our benchmark suite. Note: Rememeber to clearly describe the subset
  of the shell that we handle. To be more precise the compositional
  operator of the shell that we can handle.}

\kk{New intro sketch:}

\kk{Note: A point that we need to establish and convince the readers
  about is that the Shell IS used already for data-processing, and
  that we are not just proposing it as an alternative to other
  systems. We do not propose migrating to shell scripts if you already
  have a parallel/efficient solution. I am not sure if that needs a
  specific paragraph of its own at the start of the
  introduction. Like: ``Consider the following bash script that does
  some simple data processing... Examples like that exists in several
  domains/applications (examples, cite).''}

\begin{itemize}
\item Why is parallelism important (especially in the context of data
  processing). Significant performance benefits as most computer
  systems today have multiple processors that are under utilized
\item (Similarly to how it is now) unfortunately, it is quite hard
  reaping these benefits in contrast to sequential data
  processing. [Show Bash pipeline].
\item To benefit from parallelism, the current options are
  extreme. Either very fine-grained and low level (parallelism using
  fine-grained C libraries) for maximum performance, or very coarse
  grained and bulky where one has to use a proper big-data
  framework. (Can we fit the shell ones here (gnu-parallel, etc))
\item The common thing is that one needs to rewrite big part of their
  application, often requiring expertise and redesigning its
  architecture, in order to get benefits that in the end might not
  explain the cost.
\item To address this issue, we propose Dish, a thin layer that
  automatically! parallelizes a given shell script. Key insight is
  that a large subset of the shell language can be encoded in a
  dataflow graph model, a flexible representation that allows for
  parallelization optimizations.
\item Contributions:
\item Study of the shell primitives, identification of
  families/classes of commands that share
  distributability/parallelization properties, and a classification of
  coreutils/POSIX commands in these distributability properties.
\item Dataflow graph model that is suitable for the shell
\item A set of optimizations on this model that can be thought of as
  rewriting rules on the dataflow graph, that are sound and exploit
  parallelism.
\end{itemize}

\kk{End of new intro sketch}

@@

Distributed systems offer significant benefits over their centralized counterparts---for example, they can speed up expensive computations or can process data that would not fit into any single machine.
% offer notable benefits over their centralized counterparts:
%   using partitioning and replication, they can process and store data with increased throughput and fault-tolerance.
% Yet, only a minority of developers, employed by the select few companies that deal with massive datasets, have the luxury of engineering software systems with distribution baked in from the start.
% The remaining majority starts by developing and deploying software in a centralized manner---that is, \emph{until} there is a significant change of requirements, such as a load increase.
Despite these benefits, their development remains different from and significantly more difficult than their centralized counterparts.
Whereas anyone can quickly stitch together a Bash script to compute on a single computer, 
  % domain-experts routinely glue scripts together to process and share data. % without the help of a computing expert.
   scaling out to multiple ones requires expert labor around ``point'' solutions with expensive setups, restricted programming interfaces, and exorbitant composition costs~\cite{taurus:14, dios:13, andromeda:15, pywren:17, futuredata:18, nefele:18}.
% 
To understand this sharp contrast, consider a Bash pipeline calculating term frequencies over a set of inputs:

% \begin{lstlisting}[language=sh,float=h,numbers=none]
% cat doc.ms |                   # print input file
% groff -t -e -mandoc -Tascii |  # remove formatting
% col -bx |                      # remove backspaces 
% tr A-Z a-z |                   # convert to lower case
% tr -d '[:punct:]' |            # remove punctuation
% sort |                         # put words in alphabetical order
% unique |                       # remove duplicate words
% comm -13 /usr/share/dict -     # report words not in dictionary 
% \end{lstlisting}
% \smallskip
\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
cat * | tr -cs A-Za-z\n | tr A-Z a-z |    ($$(p_1)$$)
  sort | uniq -c | sort -rn | head 5 > out
\end{lstlisting}
% \smallskip
% \noindent
Program $p_1$ creates a character stream, breaks it into words, transliterates to lower-case, sorts to group duplicates, reduces duplicates to a counter, sorts counters in descending order, picks the top five results, and writes them to a file \ttt{out}.
Combining several features, \unix makes small tasks easy to express;
  for a user with \emph{one} computer and a small input size, this pipeline takes a few seconds to compose and execute~\cite{bentley1986literate}.
% composition allows the composition of general primitives

% Key insight 
% % The garden-hose philosophy is similar to Haskell 
% This pipeline takes an input file (line 1), removes 
% * do not need to use specialized frameworks for composition---instead, as long as they conform to the shell, individual primitives can be written in any programming language.
% * do not need to rewrite ---

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_overview.pdf}}
\caption{
  \textbf{High-level schematic.}
  \sys leverages distributability analysis for built-in commands and any developer extensions (left) to automatically transform shell scripts (mid) and orchestrates their
  execution (right).
}
\vspace{-10pt}
\label{fig:schematic}
\end{figure}

Unfortunately, developing $p_1$'s distributed equivalent requires significant effort.
% For a user with many computers and larger inputs, 
% The scope of such rewrites, and therefore the cost of manual effort, can vary considerably.
For simple pipelines, fitting into restricted models of computation, this effort amounts to expressing the computation using the primitives provided by a big-data framework~\cite{mapreduce:08, ciel:11, spark:12, naiad:13} or domain-specific language~\cite{alvaro2011consistency,distal:13,meiklejohn2015lasp}---an unjustifiable cost for small, one-off pipelines that take a few minutes to compose (but are applied to large datasets).
More complex pipelines, such as the ones presented in later sections, would involve a full-fledged distributed programming language~\cite{erlang:96, lopes1997d, acute:05, mace:07, cloudhaskell:11, ScalaLoci:18}. %  or a distributed operating system---\eg Plan9's \ttt{rc} shell.
In both cases, manual rewriting is expensive and can introduce new bugs, cascading changes, and divergence from legacy functionality.
Could the generation and execution of $p_1$'s distributed version be fully and correctly automated?

To answer this question we develop \sys, a shell variant that transforms traditional \unix pipelines into their distributed equivalents, enabling \emph{distribution-oblivious programming}.
The key insight behind \sys is that a large part of the shell language can be encoded in a distributed dataflow graph model, providing structure to distribute computations.
%% \kk{Replaced that: the language of the Unix shell already encodes stream processing, providing most of the information required to distribute a computation. }
% FIXME \kk{I am not sure whether stream processing provides information for distributing a computation on its own. Maybe we can say that the shell exposes operator level parallelism, and that this is the first step to distributing a computation}.
\sys builds on this insight with a careful study of the distributability properties of shell primitives and commands, a definition of a dataflow graph model that is suitable for the shell, a set of parallelization optimizations that preserve the behaviour of the graph, and a late-bound command-prefixing scheme for deferring scheduling decisions to the distributed planner (\ie when runtime information is available).
A \sys-enabled $p_1$ will run \ttt{tr}s on parallel streams,
  use a mostly-parallel tree of \ttt{sort}s,
  run \ttt{uniq} mostly in parallel,
  execute \ttt{head} in one of the streams,
  and (trivially) merge streams in \ttt{out}.

The combination of automated transformations for program distribution with the ability to maintain correct non-distributed semantics results in several benefits.
% \sys converts legacy shell pipelines into their distributed equivalents fully automatically, offering $100\times$ improvements in performance without a single line of additional code or annotation.
First, shell users composing pipelines (or simply running legacy pipelines on massive datasets) can see scalability benefits without any manual effort---no need for \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}, or any manual rewriting~\cite{mapreduce:08, ciel:11, spark:12}.
Second, developers of new shell commands can use a lightweight domain-specific language to express their distributability properties rather than ad-hoc, command-specific flags such as {\tt -t},  {\tt NUM\_THREADS}, \ttt{-t}, \ttt{-p} \etc
Most importantly, \sys provides an architectural lesson for system designers---namely, that large-scale efforts in the distributed- and operating-system literature to provide a \unix-like distributed equivalent~\cite{ousterhout1988sprite, mullender1990amoeba, pike1990plan9, barak1998mosix} would have been simplified by a thin (but sophisticated) rewriting shim like the one \sys provides.
% Nice critique on parallel: https://bugs.debian.org/cgi-bin/bugreport.cgi?bug=597050#75

% % Make Unix benefits explicit?
% Indeed, the primary reason behind $p_1$'s succinctness is that the pipeline is a domain-specific language for describing operations over streams.
% Key elements of \unix are the ability to compose programs written in different languages, the abstraction of a file system as a set of resident streams, a small but extensible library of commands, and the ability to resolve names within a global context.
% Under the hood, the \unix kernel buffers results, synchronizes processing stages, and generally orchestrates the computation.

The paper is structured as follows.
It starts by introducing the necessary background on shell scripting and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{impl} highlight key
contributions:
\begin{itemize}

  \item
  \S\ref{distributability} studies several distributability classes and introduces the distributability characterization language.

  \item
  \S\ref{ir} presents a dataflow graph model for encoding shell pipelines, and a set of parallelization transformations that preserve the semantics of the sequential program.

  \item
    \S\ref{impl} describes the \sys implementation and addresses
    several challenges related to the translation and optimization of
    shell programs.
    %% details other concerns, such as distributed state management and extensibility. 
\end{itemize}

\noindent
\sys's evaluation~\sx{eval} shows significant speedups (4--10$\times$) for parallel execution using a combination of real pipelines. %micro-bench\-marks %---popular shell one-liners that highlight certain features---and a multi-line macro-benchmark---a popular weather analysis script.
After a comparison with related prior work~\sx{related}, the paper closes with a discussion of limitations and possible future directions~\sx{discussion}.
% \bigskip
% \begin{quote}
% \footnotesize
Additional material, in anonymized form, is available at
\href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.
% \end{quote}

% \begin{figure*}[t]
% \centering
% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_overview.pdf}}
% \caption{
%   \textbf{Applying \sys to $p_1$.}
% }
% \label{fig:example}
% \end{figure*}
%

@@

>>>>

%% Title information
%% \title{Dish: Distribution-oblivious Shell Scripting}         %% [Short Title] is optional;
\title{DPSh: Automated Data-Parallel Processing in the Shell}         %% [Short Title] is optional;
%% \title{Extensible data processing in the shell}

@@

%% \kk{After discussion on Wednesday Jan 8: Modify the narrative of
%%   this paper to talk about data processing in the Shell. Make this
%%   the main focus of the paper. This simplifies the narrative and
%%   allows us to not talk about late planner activation as well as
%%   environment variables. It also justifies why we only deal with
%%   pure and stateless. Note that this is a very expressive model, as
%%   shown by our benchmark suite. Note: Rememeber to clearly describe
%%   the subset of the shell that we handle. To be more precise the
%%   compositional operator of the shell that we can handle.}

%% \kk{Note: A point that we need to establish early on and convince
%%   the readers about is that the Shell IS used already for
%%   data-processing, and that we are not just proposing it as an
%%   alternative to other systems. We do not propose migrating to
%%   shell scripts if you already have a parallel/efficient
%%   solution. I am not sure if that needs a specific paragraph of its
%%   own at the start of the introduction. Like: ``Consider the
%%   following bash script that does some simple data
%%   processing... Examples like that exists in several
%%   domains/applications (examples, cite).''}

%% \kk{Decide if we will mainly focus on scripts or pipelines and
%%   choose wordings appropriately.}
%
Consider the following data processing Shell script.
%% \kk{We might want to have a more complex script here.}

\begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
cat * | tr -cs A-Za-z\n | tr A-Z a-z |    ($$(p_1)$$)
  sort | uniq -c | sort -rn | head 5 > out
\end{lstlisting}

\noindent
Scripts like the one above are commonly used for orchestrating
data-processing workflows; connecting system commands with custom
tools to perform complex tasks.
%% \kk{Do we need to mention domains where that happens?}
Even though shell pipelines are designed to exploit task parallelism,
they completely ignore available data-parallelism. For small input
sizes this isn't a problem since scripts take less than a second to
execute, but as data sizes increase, failing to utilize the underlying
parallel computational resources is a significant bottleneck.

To address this concern, a Shell \emph{user} could resort to several
different solutions (e.g. gnuparallel, tsc, flags in individual
commands etc...) that offer some form of parallelism. However these
solutions are too ad-hoc (each having a disparate parallelism model),
too limited (they only apply to specific use-cases), and too
coarse-grained. \kk{Tone the previous claims down and back them up.}
At the same time, a \emph{developer} of Shell commands could rewrite
her commands using low level tools (e.g. Raftlib, openMP, etc) to
improve utilization and performance. Manual rewriting is expensive and
can introduce new bugs, cascading changes, and divergence from legacy
functionality.

To address this issue for both \emph{users} and \emph{developers}, we
propose \sys, a tool that automatically exploits available
data-parallelism in a given shell script. The key insight behind \sys
is that a large subset of the Shell language can be encoded as a
dataflow graph, a flexible representation that allows for
parallelization optimizations. \sys builds on this insight with a
careful study of the parallelizability properties of shell primitives
and commands, a definition of a dataflow graph model that is suitable
for the shell, a set of parallelization optimizations that preserve
the behaviour of the graph, and a late-bound command-prefixing scheme
for deferring optimizations as late-as-possible (\ie when runtime
information is available). \kk{Maybe elaborate some more on the
  contributions in this paragraph.}  A \sys-enabled $p_1$ will run
\ttt{tr}s on parallel streams, use a mostly-parallel tree of
\ttt{sort}s, run \ttt{uniq} mostly in parallel, execute \ttt{head} in
one of the streams, and (trivially) merge streams in \ttt{out}. The
only requirement to support a new command is that its developer adds a
lightweight annotation to describe its parallelizability properties.

The paper is structured as follows. It starts by introducing the
necessary background on shell scripting and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{impl} highlight key
contributions:
\begin{itemize}
  \item
  \S\ref{distributability} studies the parallelizability properties of
  a large class of Shell commands (coreutils) and introduces an
  lightweight annotation language for commands that could be executed
  in a data-parallel manner. \kk{Mention that we did this for all
    coreutils.}

  \item
  \S\ref{ir} presents a dataflow graph model for encoding shell
  scripts, and a set of parallelization transformations that preserve
  the semantics of the sequential program.

  \item
  \S\ref{impl} describes the \sys implementation and addresses several
  challenges related to the translation and optimization of shell
  programs. \kk{Rewrite that when we know for sure what the section
    contains.}

\end{itemize}

\noindent
\sys's evaluation~\sx{eval} shows significant speedups (4--10$\times$)
for parallel execution using a combination of real pipelines.
%micro-bench\-marks %---popular shell one-liners that highlight
%certain features---and a multi-line macro-benchmark---a popular
%weather analysis script.
After a comparison with related prior work~\sx{related}, the paper
closes with a discussion of limitations and possible future
directions~\sx{discussion}.
%% Additional material, in anonymized form, is available at
%% \href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.

@@

Key tasks, in rough order of importance:
  (i) change title and intro to avoid distribution
  (ii) cleanup and rewrite sections 4, 5: introduce our high-level figure, talk
  about things in order, add ordering in graphs, generally refine and beautify
  as much as possible.
  (iii) tighten section 2, everything in there has to be related to some part of
  the story---make the connection explicit
  (iv) Pump up evaluation: could we add 3 more micro-benchmarks? could we add
  1--2 more macro-benchmarks?
  (v) since this is IFCP, could we add some simple semantics and derivation
  rules? we should certainly be able to describe some of the optimizations as
  congruence rules.
  (vi) complete the related work with some operating-systems literature.
  --------
%   Need to highlight the use of ad-hoc flags
%   Need to highlight use cases / goals:
%     still POSIX compliant, you can replace /bin/bash with /bin/dish and see
%     \emph{some} performance improvements, even if we can't handle all cases
%     today--that is, dish enables a platform for further research.
%
%  Talk about order-aware dataflow analysis?
}

%% \kk{Begin of new intro sketch}
%% \begin{itemize}
%% \item Why is parallelism important (especially in the context of data
%%   processing). Significant performance benefits as most computer
%%   systems today have multiple processors that are under utilized
%% \item (Similarly to how it is now) unfortunately, it is quite hard
%%   reaping these benefits in contrast to sequential data
%%   processing. [Show Bash pipeline].
%% \item To benefit from parallelism, the current options are
%%   extreme. Either very fine-grained and low level (parallelism using
%%   fine-grained C libraries) for maximum performance, or very coarse
%%   grained and bulky where one has to use a proper big-data
%%   framework. (Can we fit the shell ones here (gnu-parallel, etc))
%% \item The common thing is that one needs to rewrite big part of their
%%   application, often requiring expertise and redesigning its
%%   architecture, in order to get benefits that in the end might not
%%   explain the cost.
%% \item To address this issue, we propose Dish, a thin layer that
%%   automatically! parallelizes a given shell script. Key insight is
%%   that a large subset of the shell language can be encoded in a
%%   dataflow graph model, a flexible representation that allows for
%%   parallelization optimizations.
%% \end{itemize}
%% Contributions:
%% \begin{itemize}
%% \item Study of the shell primitives, identification of
%%   families/classes of commands that share
%%   distributability/parallelization properties, and a classification of
%%   coreutils/POSIX commands in these distributability properties.
%% \item Dataflow graph model that is suitable for the shell
%% \item A set of optimizations on this model that can be thought of as
%%   rewriting rules on the dataflow graph, that are sound and exploit
%%   parallelism.
%% \end{itemize}
%% \kk{End of new intro sketch}

@@

%% Distributed systems offer significant benefits over their centralized counterparts---for example, they can speed up expensive computations or can process data that would not fit into any single machine.
%% % offer notable benefits over their centralized counterparts:
%% %   using partitioning and replication, they can process and store data with increased throughput and fault-tolerance.
%% % Yet, only a minority of developers, employed by the select few companies that deal with massive datasets, have the luxury of engineering software systems with distribution baked in from the start.
%% % The remaining majority starts by developing and deploying software in a centralized manner---that is, \emph{until} there is a significant change of requirements, such as a load increase.
%% Despite these benefits, their development remains different from and significantly more difficult than their centralized counterparts.
%% Whereas anyone can quickly stitch together a Bash script to compute on a single computer, 
%%   % domain-experts routinely glue scripts together to process and share data. % without the help of a computing expert.
%%    scaling out to multiple ones requires expert labor around ``point'' solutions with expensive setups, restricted programming interfaces, and exorbitant composition costs~\cite{taurus:14, dios:13, andromeda:15, pywren:17, futuredata:18, nefele:18}.
%% % 
%% To understand this sharp contrast, consider a Bash pipeline calculating term frequencies over a set of inputs:

%% % \begin{lstlisting}[language=sh,float=h,numbers=none]
%% % cat doc.ms |                   # print input file
%% % groff -t -e -mandoc -Tascii |  # remove formatting
%% % col -bx |                      # remove backspaces 
%% % tr A-Z a-z |                   # convert to lower case
%% % tr -d '[:punct:]' |            # remove punctuation
%% % sort |                         # put words in alphabetical order
%% % unique |                       # remove duplicate words
%% % comm -13 /usr/share/dict -     # report words not in dictionary 
%% % \end{lstlisting}
%% % \smallskip
%% \begin{lstlisting}[language=sh, float=h, numbers=none, escapeinside={($}{$)}]
%% cat * | tr -cs A-Za-z\n | tr A-Z a-z |    ($$(p_1)$$)
%%   sort | uniq -c | sort -rn | head 5 > out
%% \end{lstlisting}
%% % \smallskip
%% % \noindent
%% Program $p_1$ creates a character stream, breaks it into words, transliterates to lower-case, sorts to group duplicates, reduces duplicates to a counter, sorts counters in descending order, picks the top five results, and writes them to a file \ttt{out}.
%% Combining several features, \unix makes small tasks easy to express;
%%   for a user with \emph{one} computer and a small input size, this pipeline takes a few seconds to compose and execute~\cite{bentley1986literate}.
%% % composition allows the composition of general primitives

%% % Key insight 
%% % % The garden-hose philosophy is similar to Haskell 
%% % This pipeline takes an input file (line 1), removes 
%% % * do not need to use specialized frameworks for composition---instead, as long as they conform to the shell, individual primitives can be written in any programming language.
%% % * do not need to rewrite ---

%% \begin{figure}[t]
%% \centering
%% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_overview.pdf}}
%% \caption{
%%   \textbf{High-level schematic.}
%%   \sys leverages distributability analysis for built-in commands and any developer extensions (left) to automatically transform shell scripts (mid) and orchestrates their
%%   execution (right).
%% }
%% \vspace{-10pt}
%% \label{fig:schematic}
%% \end{figure}

%% Unfortunately, developing $p_1$'s distributed equivalent requires significant effort.
%% % For a user with many computers and larger inputs, 
%% % The scope of such rewrites, and therefore the cost of manual effort, can vary considerably.
%% For simple pipelines, fitting into restricted models of computation, this effort amounts to expressing the computation using the primitives provided by a big-data framework~\cite{mapreduce:08, ciel:11, spark:12, naiad:13} or domain-specific language~\cite{alvaro2011consistency,distal:13,meiklejohn2015lasp}---an unjustifiable cost for small, one-off pipelines that take a few minutes to compose (but are applied to large datasets).
%% More complex pipelines, such as the ones presented in later sections, would involve a full-fledged distributed programming language~\cite{erlang:96, lopes1997d, acute:05, mace:07, cloudhaskell:11, ScalaLoci:18}. %  or a distributed operating system---\eg Plan9's \ttt{rc} shell.
%% In both cases, manual rewriting is expensive and can introduce new bugs, cascading changes, and divergence from legacy functionality.
%% Could the generation and execution of $p_1$'s distributed version be fully and correctly automated?

%% To answer this question we develop \sys, a shell variant that transforms traditional \unix pipelines into their distributed equivalents, enabling \emph{distribution-oblivious programming}.
%% The key insight behind \sys is that a large part of the shell language can be encoded in a distributed dataflow graph model, providing structure to distribute computations.
%% %% \kk{Replaced that: the language of the Unix shell already encodes stream processing, providing most of the information required to distribute a computation. }
%% % FIXME \kk{I am not sure whether stream processing provides information for distributing a computation on its own. Maybe we can say that the shell exposes operator level parallelism, and that this is the first step to distributing a computation}.
%% \sys builds on this insight with a careful study of the distributability properties of shell primitives and commands, a definition of a dataflow graph model that is suitable for the shell, a set of parallelization optimizations that preserve the behaviour of the graph, and a late-bound command-prefixing scheme for deferring scheduling decisions to the distributed planner (\ie when runtime information is available).
%% A \sys-enabled $p_1$ will run \ttt{tr}s on parallel streams,
%%   use a mostly-parallel tree of \ttt{sort}s,
%%   run \ttt{uniq} mostly in parallel,
%%   execute \ttt{head} in one of the streams,
%%   and (trivially) merge streams in \ttt{out}.

%% % Developers of commands
%% % Developers of pipelines
%% % Language unifies both---no need for `-t` `-p`
%% % POSIX:
%%   % https://pubs.opengroup.org/onlinepubs/009695399/utilities/xcu_chap02.html

%% The combination of automated transformations for program distribution with the ability to maintain correct non-distributed semantics results in several benefits.
%% % \sys converts legacy shell pipelines into their distributed equivalents fully automatically, offering $100\times$ improvements in performance without a single line of additional code or annotation.
%% First, shell users composing pipelines (or simply running legacy pipelines on massive datasets) can see scalability benefits without any manual effort---no need for \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}, or any manual rewriting~\cite{mapreduce:08, ciel:11, spark:12}.
%% Second, developers of new shell commands can use a lightweight domain-specific language to express their distributability properties rather than ad-hoc, command-specific flags such as {\tt -t},  {\tt NUM\_THREADS}, \ttt{-t}, \ttt{-p} \etc
%% Most importantly, \sys provides an architectural lesson for system designers---namely, that large-scale efforts in the distributed- and operating-system literature to provide a \unix-like distributed equivalent~\cite{ousterhout1988sprite, mullender1990amoeba, pike1990plan9, barak1998mosix} would have been simplified by a thin (but sophisticated) rewriting shim like the one \sys provides.
%% % Nice critique on parallel: https://bugs.debian.org/cgi-bin/bugreport.cgi?bug=597050#75

%% % % Make Unix benefits explicit?
%% % Indeed, the primary reason behind $p_1$'s succinctness is that the pipeline is a domain-specific language for describing operations over streams.
%% % Key elements of \unix are the ability to compose programs written in different languages, the abstraction of a file system as a set of resident streams, a small but extensible library of commands, and the ability to resolve names within a global context.
%% % Under the hood, the \unix kernel buffers results, synchronizes processing stages, and generally orchestrates the computation.

%% The paper is structured as follows.
%% It starts by introducing the necessary background on shell scripting and overviewing \sys~\sx{bg}.
%% Sections \ref{distributability}--\ref{impl} highlight key
%% contributions:
%% \begin{itemize}

%%   \item
%%   \S\ref{distributability} studies several distributability classes and introduces the distributability characterization language.

%%   \item
%%   \S\ref{ir} presents a dataflow graph model for encoding shell pipelines, and a set of parallelization transformations that preserve the semantics of the sequential program.

%%   \item
%%     \S\ref{impl} describes the \sys implementation and addresses
%%     several challenges related to the translation and optimization of
%%     shell programs.
%%     %% details other concerns, such as distributed state management and extensibility. 
%% \end{itemize}

%% \noindent
%% \sys's evaluation~\sx{eval} shows significant speedups (4--10$\times$) for parallel execution using a combination of real pipelines. %micro-bench\-marks %---popular shell one-liners that highlight certain features---and a multi-line macro-benchmark---a popular weather analysis script.
%% After a comparison with related prior work~\sx{related}, the paper closes with a discussion of limitations and possible future directions~\sx{discussion}.
%% % \bigskip
%% % \begin{quote}
%% % \footnotesize
%% Additional material, in anonymized form, is available at
%% \href{https://git.io/Je6Nk}{https://git.io/Je6Nk}.
%% % \end{quote}

%% % \begin{figure*}[t]
%% % \centering
%% % \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_overview.pdf}}
%% % \caption{
%% %   \textbf{Applying \sys to $p_1$.}
%% % }
%% % \label{fig:example}
%% % \end{figure*}
%% %

@@

\kk{Maybe guide all of this by showing an example of an output shell
  script?}
